### 2025-03-27 ms/response_letter.qmd

---
author: ""
fontsize: 12pt
format:
  pdf:
    keep-tex: true
    latex-clean: false
    pdf-engine: xelatex
    include-in-header:
      text: |
        \usepackage[default]{sourcesanspro}
        \usepackage{sourcecodepro}
        \usepackage{xcolor}
        \usepackage{mdframed}
        % Define blockquote colors
        \definecolor{blockquote-border}{RGB}{221,221,221}
        \definecolor{blockquote-text}{RGB}{119,119,119}
        % Define custom blockquote environment
        \newmdenv[
          rightline=false,
          bottomline=false,
          topline=false,
          linewidth=3pt,
          linecolor=blockquote-border,
          skipabove=\parskip,
          innerleftmargin=10pt,
          innerrightmargin=0pt,
          frametitlebackgroundcolor=gray!20
        ]{customblockquote}
        \renewenvironment{quote}
          {\begin{customblockquote}\color{blockquote-text}\ignorespaces}
          {\end{customblockquote}}
  html:
    theme: coderpro
    toc: true
    toc-depth: 2
    number-sections: true
    smooth-scroll: true
    standalone: true
    embed-resources: true
---

@@

> 2) Abstract is informative and it reflects the body of the paper.

We appreciate your positive feedback on the abstract.

> 3) The objectives must be modified for a better understanding of the reader.

Thank you for your suggestion.
We have revised the Introduction to clearly state the main objective of the study before presenting the specific questions (line 117-119).

@@

> 4) Line 366-369 & Table 2: In the sentence "In addition, the estimated exponent aligns closely with MST predictions for crown radius, supporting the selection of the power-law model for angiosperms, where the community-level exponent b is near the expected *2/3* ($b_{ang}$=0.625775 0.6168636,0.6345041, Table 2)" and the parameter estimates in Table 2, the values are not consistently presented. Check whole of the manuscript for a uniform presentation of the values.

We have standardized the presentation of all parameter estimates throughout the manuscript, including Table 2 and Tables S6-8 and corresponding text.

@@

> 5) Table 1: The table does not clearly explain how much of a difference in ΔLOOIC is considered significant between the two models.

We have revised the caption of Table 1 to clarify that a $\Delta$LOOIC greater than 4 suggests a meaningful difference in predictive performance (line 262-264).

@@

> 6) Figure S1: According to the supplementary materials section, the figure is incorrectly labeled Figure 1. It should be Figure S1.

We have corrected the figure label.

> 7) The reference section was informative. However, incorporate some latest references and arrange them according to the journal guidelines.

We have updated the references with recent publications, including Tavankar et al. (2019), Murphy and Bradford (2022), Fajardo et al. (2022), Cochrane et al. (2023), Sivula et al. (2023), and formatted them according to the journal guidelines.

@@

> 8) Supplementary Table S6 is very congested and hard to read. Please revise for better understanding.

We have reformatted Supplementary Tables S6, S7, and S8 for improved readability and included detailed captions to aid interpretation.

> 9) A revision of the English is needed as some sentences aren't properly structured, and it's often difficult to grasp what the authors are saying.

We have revised the manuscript for language, grammar, and sentence structure to enhance clarity and improve overall readability.
For example, we revised lines 481–486 in the Discussion section to ensure sentence brevity and clarity.
Additionally, we updated the figure legends and table captions for greater clarity and carefully cross-checked all technical terms to maintain consistency throughout the text.

@@

> Reviewer #5: Congratulations on a well-written and clear manuscript. Your approach to exploring allometric relationships between DBH, height, wood density, biomass, and crown radius is highly interesting and contributes significantly to the field. While I primarily focus on the data analysis section and found no major concerns, I would like to suggest a few minor corrections and discussion points.

Thank you so much for your encouraging and constructive feedback.

> 1) In Figure 3, the distinction between species with light and dense wood density is presented. However, the criteria used for this classification are not mentioned in the Materials and Methods section. Clarifying this would improve the transparency of your methodology.

Thank you for pointing this out.
We have added a description in the Methods section clarifying the classification criteria (line 197-202).

@@

> 2) Figure 4 appears to have a formatting issue, as the letters 'a' and 'd' are not displayed.

We were unable to see the absence of the letters "a" and "d" in Figure 4 of the submitted manuscript, so we are unsure how to address this issue.
Nevertheless, we slightly increased the left margin of the panel labels in case clipping was the cause.

@@

> 3) It may be valuable to discuss the potential confounding effects of environmental factors on observed allometric correlations when considering wood density. Given intraspecific variation, wood density may not have a strong impact on those allometric relationships, since Fajardo et al. (2022) suggest that wood density is more closely linked to vessel anatomy than to tree architecture within the same species across different environments.

We agree with your point and have expanded the Discussion section to address potential environmental confounding effects.
We also cited Fajardo et al. (2022) to highlight less clear linkages between tree architecture and intraspecific variation in wood density  (line 437-444).

@@

> 4) I found the "Consequences for AGB Estimates" section particularly insightful.

Thank you for your positive feedback.

> 5) Pages 132-140 are blank, likely due to a formatting issue with the final table. The table appears to have fixed columns that prevent the complete display of cell information.

We have resolved the formatting issue of Tables S6–S8 that may have caused the blank pages in the supplementary file.
These tables, which were submitted as Excel files, were included in the PDF due to a system-related submission setting.

### 2025-03-27 ms/response_letter.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  12pt,
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage[default]{sourcesanspro}
\usepackage{sourcecodepro}
\usepackage{xcolor}
\usepackage{mdframed}
% Define blockquote colors
\definecolor{blockquote-border}{RGB}{221,221,221}
\definecolor{blockquote-text}{RGB}{119,119,119}
% Define custom blockquote environment
\newmdenv[
  rightline=false,
  bottomline=false,
  topline=false,
  linewidth=3pt,
  linecolor=blockquote-border,
  skipabove=\parskip,
  innerleftmargin=10pt,
  innerrightmargin=0pt,
  frametitlebackgroundcolor=gray!20
]{customblockquote}
\renewenvironment{quote}
  {\begin{customblockquote}\color{blockquote-text}\ignorespaces}
  {\end{customblockquote}}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, interior hidden, boxrule=0pt, frame hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi

March xxx, 2025

@@

On behalf of the authors: Thi Duyen Nguyen

Corresponding author and contact information: Key Laboratory of Tropical
Forest Ecology, Xishuangbanna Tropical Botanical Garden, Chinese Academy
of Sciences, Mengla, Yunnan 666303, China\\
Email: katabuchi@xtbg.ac.cn; mattocci27@gmail.com

\newpage

\hypertarget{responses}{%
\section{Responses}\label{responses}}

@@

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{3}
\tightlist
\item
  Line 366-369 \& Table 2: In the sentence ``In addition, the estimated
  exponent aligns closely with MST predictions for crown radius,
  supporting the selection of the power-law model for angiosperms, where
  the community-level exponent b is near the expected \emph{2/3}
  (\(b_{ang}\)=0.625775 0.6168636,0.6345041, Table 2)'' and the
  parameter estimates in Table 2, the values are not consistently
  presented. Check whole of the manuscript for a uniform presentation of
  the values.
\end{enumerate}
\end{quote}

We have standardized the presentation of all parameter estimates
throughout the manuscript, including Table 2 and Tables S6-8 and
corresponding text.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{4}
\tightlist
\item
  Table 1: The table does not clearly explain how much of a difference
  in ΔLOOIC is considered significant between the two models.
\end{enumerate}
\end{quote}

We have revised the caption of Table 1 to clarify that a \(\Delta\)LOOIC
greater than 4 suggests a meaningful difference in predictive
performance (line 262-264).

@@

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{5}
\tightlist
\item
  Figure S1: According to the supplementary materials section, the
  figure is incorrectly labeled Figure 1. It should be Figure S1.
\end{enumerate}
\end{quote}

We have corrected the figure label.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{6}
\tightlist
\item
  The reference section was informative. However, incorporate some
  latest references and arrange them according to the journal
  guidelines.
\end{enumerate}
\end{quote}

We have updated the references with recent publications, including
Tavankar et al.~(2019), Murphy and Bradford (2022), Fajardo et
al.~(2022), Cochrane et al.~(2023), Sivula et al.~(2023), and formatted
them according to the journal guidelines.

@@

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{7}
\tightlist
\item
  Supplementary Table S6 is very congested and hard to read. Please
  revise for better understanding.
\end{enumerate}
\end{quote}

We have reformatted Supplementary Tables S6, S7, and S8 for improved
readability and included detailed captions to aid interpretation.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{8}
\tightlist
\item
  A revision of the English is needed as some sentences aren't properly
  structured, and it's often difficult to grasp what the authors are
  saying.
\end{enumerate}
\end{quote}

We have revised the manuscript for language, grammar, and sentence
structure to enhance clarity and improve overall readability. For
example, we revised lines 481--486 in the Discussion section to ensure
sentence brevity and clarity. Additionally, we updated the figure
legends and table captions for greater clarity and carefully
cross-checked all technical terms to maintain consistency throughout the
text.

@@

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  In Figure 3, the distinction between species with light and dense wood
  density is presented. However, the criteria used for this
  classification are not mentioned in the Materials and Methods section.
  Clarifying this would improve the transparency of your methodology.
\end{enumerate}
\end{quote}

Thank you for pointing this out. We have added a description in the
Methods section clarifying the classification criteria (line 197-202).

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  Figure 4 appears to have a formatting issue, as the letters `a' and
  `d' are not displayed.
\end{enumerate}
\end{quote}

We were unable to see the absence of the letters ``a'' and ``d'' in
Figure 4 of the submitted manuscript, so we are unsure how to address
this issue. Nevertheless, we slightly increased the left margin of the
panel labels in case clipping was the cause.

@@

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{2}
\tightlist
\item
  It may be valuable to discuss the potential confounding effects of
  environmental factors on observed allometric correlations when
  considering wood density. Given intraspecific variation, wood density
  may not have a strong impact on those allometric relationships, since
  Fajardo et al.~(2022) suggest that wood density is more closely linked
  to vessel anatomy than to tree architecture within the same species
  across different environments.
\end{enumerate}
\end{quote}

We agree with your point and have expanded the Discussion section to
address potential environmental confounding effects. We also cited
Fajardo et al.~(2022) to highlight less clear linkages between tree
architecture and intraspecific variation in wood density (line 437-444).

@@

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{3}
\tightlist
\item
  I found the ``Consequences for AGB Estimates'' section particularly
  insightful.
\end{enumerate}
\end{quote}

Thank you for your positive feedback.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{4}
\tightlist
\item
  Pages 132-140 are blank, likely due to a formatting issue with the
  final table. The table appears to have fixed columns that prevent the
  complete display of cell information.
\end{enumerate}
\end{quote}

We have resolved the formatting issue of Tables S6--S8 that may have
caused the blank pages in the supplementary file. These tables, which
were submitted as Excel files, were included in the PDF due to a
system-related submission setting.

### 2025-03-27 ms/ms.qmd
typo

MK was supported by
the Xingdian Talenj Support Program of Yunnan Province,
the Xishuangbanna State Rainforest Talent Support Program (E4BN041B01), and
the CAS President's International Fellowship Initiative (2020FYB0003).

>>>>

MK was supported by
the Xingdian Talent Support Program of Yunnan Province,
the Xishuangbanna State Rainforest Talent Support Program (E4BN041B01), and
the CAS President's International Fellowship Initiative (2020FYB0003).

### 2025-03-27 ms/ms.tex
typo

\begin{document}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, enhanced, sharp corners, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi

@@

MK was supported by the Xingdian Talenj Support Program of Yunnan
Province, the Xishuangbanna State Rainforest Talent Support Program
(E4BN041B01), and the CAS President's International Fellowship
Initiative (2020FYB0003).

>>>>

\begin{document}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, enhanced, breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

@@

MK was supported by the Xingdian Talent Support Program of Yunnan
Province, the Xishuangbanna State Rainforest Talent Support Program
(E4BN041B01), and the CAS President's International Fellowship
Initiative (2020FYB0003).

\hypertarget{data-availability}{%
\section*{Data availability}\label{data-availability}}
\addcontentsline{toc}{section}{Data availability}

Tallo and TRY data are available from their respective platforms. Codes
are available from Zenodo at xxx
